\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Adityaa Saha}} \\
    \vspace{2pt}
    23cs01002@iitbbs.ac.in \;|\; 
    \href{https://github.com/Adityaa-Saha17}{github} \;|\;
    \href{https://www.linkedin.com/in/adityaa-saha-533b02299}{linkedin}
\end{center}

\vspace{8pt}

\textbf{Technical Skills} \\
\hrule
\vspace{4pt}
\textbf{Programming Languages:} C, C++, JavaScript, TypeScript, Python \\
\textbf{Web Technologies:} HTML, CSS, React, Node.js, Express \\
\textbf{Databases:} MySQL, MongoDB \\
\textbf{Tools \& Platforms:} Git, GitHub, VS Code \\
\textbf{Core Concepts:} Data Structures, Algorithms, OOP, Computer Architecture

\vspace{10pt}

\textbf{Projects} \\
\hrule
\vspace{4pt}

\textbf{32-bit RISC-V CPU Simulator} \hfill C/C++ \\
\begin{itemize}
    \item Designed and implemented a 32-bit pipelined RISC-V processor simulator compliant with the RV32I instruction set.
    \item Built a 5-stage pipeline (IF, ID, EX, MEM, WB) with hazard detection and data forwarding.
    \item Simulated instruction execution, pipeline stalls, and forwarding logic to ensure correctness.
\end{itemize}
\href{https://github.com/Adityaa-Saha17/32-bit-RISC-V-CPU-Simulator.git}{GitHub Repository}

\vspace{6pt}

\textbf{Log-Structured Merge (LSM) Tree Implementation (In Progress)} \hfill C++ \\
\begin{itemize}
    \item Implemented a disk-based key-value store using the Log-Structured Merge (LSM) Tree architecture.
    \item Designed core components including MemTable, SSTables, and compaction mechanism.
    \item Integrated write-ahead logging (WAL) for durability and crash recovery.
    \item Used CRC32 checksums to ensure data integrity during storage and retrieval.
    \item Optimized read/write performance using sequential disk access and sorted structures.
\end{itemize}
\href{https://github.com/Adityaa-Saha17/Log-Structured-Merge-Tree}{GitHub Repository}

\vspace{6pt}

\textbf{Social Media Application (In Progress)} \hfill Node.js, Express, MongoDB \\
\begin{itemize}
    \item Developing a full-stack social media platform with authentication and authorization.
    \item Implementing features such as posts, likes, comments, and user profiles.
    \item Designing REST APIs and managing data using MongoDB.
\end{itemize}
\href{https://github.com/Adityaa-Saha17/Social-Media-App-Backend.git}{GitHub Repository — Backend}

\vspace{6pt}

\textbf{Library Management System} \hfill React, Node.js, Express, MySQL \\
\begin{itemize}
    \item Built the complete frontend in React for a full-stack library management web application as part of a team project.
    \item Implemented UI for book browsing, search, and borrowing workflows with integration to RESTful backend APIs.
    \item Collaborated with a backend partner responsible for the Node.js/Express server and relational MySQL schema.
\end{itemize}
\href{https://github.com/Adityaa-Saha17/DBS-Project-Spring-2026-frontend.git}{GitHub Repository — Frontend} \;|\;
\href{https://github.com/jeeban-jyoti/DBS-Project-Spring-2026.git}{GitHub Repository — Backend}

\vspace{6pt}

\textbf{Multi-Client Chat System} \hfill C, Socket Programming \\
\begin{itemize}
    \item Implemented a concurrent multi-client chat server and client in C using TCP sockets and the POSIX networking API.
    \item Designed the server to handle multiple simultaneous client connections using threads.
    \item Supported broadcast messaging across all connected clients with a lightweight custom protocol.
\end{itemize}
\href{https://github.com/Adityaa-Saha17/Multi-Chat-System.git}{GitHub Repository}

\vspace{10pt}

\textbf{Education} \\
\hrule
\vspace{4pt}
\textbf{Indian Institute of Technology Bhubaneswar} \hfill 2023 -- 2027 \\
B.Tech in Computer Science and Engineering

\vspace{10pt}

\textbf{Positions of Responsibility} \\
\hrule
\vspace{4pt}
\begin{itemize}
    \item Core Member, Dramatics Society — The Fourth Wall
    \item Event Management Team Member, Cultural Fest — Alma Fiesta
\end{itemize}

\vspace{10pt}

\textbf{Extracurricular Activities} \\
\hrule
\vspace{4pt}
\begin{itemize}
    \item Member of the IIT Bhubaneswar football team
    \item Active involvement in dramatics and stage performances
\end{itemize}

\vspace{10pt}

\textbf{Achievements} \\
\hrule
\vspace{4pt}
\begin{itemize}
    \item Secured 2nd Place in Inter-Branch General Championship (Game Development)
\end{itemize}

\vspace{10pt}

\textbf{Interests} \\
\hrule
\vspace{4pt}
Data Structures and Algorithms, Systems Programming, Backend Development

\end{document}